HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-14 draft/ms_v1.tex
Song: CModel color & astrometry

%% ------------------------------------------------------------------------------------ %%
%% Fig: Color-Color Distributions of the Input and Measurements for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_cdist}
    \end{center}
    \caption{
        Evaluations of the accuracy of color measurements for synthetic galaxies
        using the color-color distributions.
        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one
        uses $(i-z)$ and $(z-y)$ colors.
        The filled contours and shaded histograms reflect the distributions for input
        colors.
        The empty contours and solid-line histograms show the distributions recovered
        by \hscpipe{} \cmodel{} photometry.
        }
    \label{fig:galaxy_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

\subsubsection{Input magnitude and the \s2n{} of \cmodel{} photometry}

@@

    We still use $i$- and $g$-band as examples. 
    Comparing to the similar figure for stars, the most obvious difference is that
    at fixed input magnitude, the \s2n{} distribution of galaxies show much larger
    scatter than stars.  
    At the same total flux, galaxy can have different size and shape, and 
    naturally leads to differences in their peak and average \s2n{}.  
    This also makes it difficult to have a clear definition of ``detection limit'' 
    for galaxies. 
    For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit 
    of our sample ($25.2$ mag) is ${\sim}20$, but the low-\s2n{} tail has already 
    reached to the \s2n{}$=5$ boundary.  
    This suggests that, although HSC Wide can detect galaxies as faint as 
    $i{\sim}26.0$ mag, the sample will become highly incomplete. 
    Furthermore, it can also introduce bias into the selection as galaxies with 
    certain structural properties are harder to detect than others. 
    \todo{Add average \s2n{} of the high and low \ser{} index galaxies at 
    $23.8 < i < 24.2$ mag.}
    Users of HSC survey data who want to select flux-limited samples of galaxies,
    or intend to study the population of faint (e.g. high-$z$) galaxies should
    keep this in mind.

@@

\subsubsection{Accuracy of the \cmodel{} magnitude}

@@

\subsubsection{Accuracy of the \cmodel{} color}

        \item \plan{Briefly explain why \cmodel{} colors are important.}

        \item The results for accuracy of \forced{} \cmodel{} colors are shown in
            Fig \ref{fig:cmodel_color} and Fig \ref{fig:cmodel_cdist}.

        \item \plan{\forced{} \cmodel{} photometry provides accurate and unbiased
            colors for galaxies at $20.0 < i < 25.0$ mag at different seeing conditions.
            The accuracies of colors also do not show dependence on input colors.
            }

        \item \plan{For $(g-i)$ color, average uncertainty around
            $i_{\mathrm{Input}}{\sim}21.0$ mag is ${\sim}0.04$ mag.
            The uncertainty increases to ${\sim}0.11$ mag at
            $i_{\mathrm{Input}}{\sim}25.0$ mag.
            Results for $(i-y)$ color is similar.}

        \item \plan{High blendedness can increase the uncertainties of the color
            and bias the color measurements.
            The highly blended galaxies on average show slightly bluer $(g-i)$ colors
            and redder $(i-y)$ colors comparing to the input values.}

        \item \plan{In Fig \ref{fig:cmodel_cdist}, we show that the \forced{} \cmodel{}
            photometry can reasonably recover the color-color distributions of galaxies
            down to $i{\sim}25$ mag.
            }

@@

\section{Results on Other Performance}
    \label{sec:others}

@@

        \item \plan{Explain what we are testing here; and why it is useful}

        \item In Fig \ref{fig:astrometry}, we briefly look into the accuracies
            of the astrometric comparison for both synthetic stars and galaxies in
            \tracts{} with both good and bad seeing.

        \item \plan{We see small astrometric offsets in both R.A and Dec directions
            that show small differences between the two \tracts{}.
            The average offset is at ${\sim}10$--20 mas, which is consistent with
            the estimate in \citet{HSCDR1}}.

@@

>>>>

%% ------------------------------------------------------------------------------------ %%
%% Fig: Color-Color Distributions of the Input and Measurements for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_cdist}
    \end{center}
    \caption{
        Evaluations of the accuracy of color measurements for synthetic galaxies
        using the color-color distributions.
        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one
        uses $(i-z)$ and $(z-y)$ colors.
        The filled contours and shaded histograms reflect the distributions for input
        colors.
        The empty contours and solid-line histograms show the distributions recovered
        by \hscpipe{} \cmodel{} photometry.
        }
    \label{fig:cmodel_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Input magnitude and the \s2n{} of \cmodel{} photometry}

@@

    We still use $i$- and $g$-band as examples. 
    Comparing to the similar figure for stars, the most obvious difference is that
    at fixed input magnitude, the \s2n{} distribution of galaxies show much larger
    scatter than stars.  
    At the same total flux, galaxy can have different size and shape, and 
    naturally leads to differences in their peak and average \s2n{}.  
    This also makes it difficult to have a clear definition of ``detection limit'' 
    for galaxies. 
    For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit 
    of our sample ($25.2$ mag) is ${\sim}20$, but the low-\s2n{} tail has already 
    reached to the \s2n{}$=5$ boundary.  
    This suggests that, although HSC Wide can detect galaxies as faint as 
    $i{\sim}26.0$ mag, the sample will become highly incomplete. 
    Furthermore, it can also introduce bias into the selection as galaxies with 
    certain structural properties are harder to detect than others. 
    Users of HSC survey data who want to select flux-limited samples of galaxies,
    or intend to study the population of faint (e.g. high-$z$) galaxies should
    keep this in mind.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of the \cmodel{} magnitude}

@@

%% ------------------------------------------------------------------------------------ %%   
\subsubsection{Accuracy of the \cmodel{} color}

    The consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial 
    to the photometric redshift and spectral energy distribution (SED) fitting results. 
    They are also key to the selection of high-$z$ Lyman-break galaxies (LBG) and 
    and many other interesting objects.

    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars 
    (Fig \ref{fig:psf_color}).
    These plots show that \hscpipe{} can provide reliable \cmodel{} colors for 
    synthetic galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag. 
    For $(g-i)$ colors, average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag 
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    Results for $(i-y)$ colors are similar.

    The performance of \forced{} \cmodel{} color does not show dependence on seeing
    condition, and is unbiased across the ranges for input total magnitude and color.
    The only noticeable feature is that the $(i-y)$ color at 
    $i_{\mathrm{Input}}>24.0$ is slightly overestimated. 
    As mentioned above, this is not surprise given the shallower imaging depth of 
    $y$-band.    
    At the same time, high blendedness of synthetic galaxies can still increase the 
    uncertainties of the color and bias the color measurements.
    The highly blended galaxies on average show slightly bluer $(g-i)$ 
    colors and redder $(i-y)$ colors than the input values.

    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions 
    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}. 
    The general distributions of colors are well recovered despite the accuracy is 
    not as good as the one for stars, especially on the $(i-z)$ v.s. $(z-y)$ plane. 
    It is expected given the narrow dynamical ranges of these colors among red filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$ 
    colors at the very ``blue'' end, while overestimate the $(i-y)$ color at very 
    red end.

    In the end, we should point out that we assume constant color for the entire galaxy.  
    In reality, different colors for individual components and smooth color gradient 
    can really complicated the situation, hence the uncertainties of \cmodel{} colors 
    here should be considered as lower limits.
%% ------------------------------------------------------------------------------------ %%

@@

\section{Results on Other Aspects of \hscpipe{}}
    \label{sec:others}

    In this section, we briefly discuss a few other issues of \hscpipe{} that relates 
    to astrometric calibration, star-galaxy separation, and measurements of galaxy 
    shape to demonstrate the ranges of topics can be tested by \synpipe{}

@@

    For \synpipe{} test, we inject synthetic objects to single \visit{} images using 
    the less accurate, initial astrometric calibration. 
    During the image stacking step, the joint calibration process will improve the 
    astrometric solutions. 
    Therefore the differences between the input and output coordinates from \synpipe{}
    can help understand the systematic effect of this step.

    In Fig \ref{fig:astrometry}, we plot the distributions of astrometric offsets for 
    both synthetic stars and galaxies in good- and bad-seeing \tracts{}. 
    Small systematic offsets at ${\sim}10$--20 mas can be noticed in either direction. 
    The two \tracts{} apparently show different systematic offsets. 
    In the same \tracts{}, synthetic stars and galaxies show very similar offsets, 
    although the scatter for galaxies is slightly larger due to their extended nature.

@@

    As we already mentioned, star--galaxy separation is important for cosmology survey,
    and becomes increasingly difficult for fainter and fainter objects.
